---
title: "R Markdown and Leaflet"
author: "Rudra Patel"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objectives
Create a web page using R Markdown that features a map created with Leaflet. Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

#Review Criteria
The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?

```{r System Time}
Sys.time()
```

```{r System Date}
Sys.Date()
```

Does the web page feature an interactive map that appears to have been created with Leaflet?

I will show in the map my top 5 cities to do vacations in Europe.

```{r map}
library(leaflet)

Urlaub <- leaflet()
Urlaub <- addTiles(Urlaub)
Urlaub <- addMarkers(Urlaub, lng=77.23, lat=28.61, popup="Delhi, India")
Urlaub <- addMarkers(Urlaub, lng=72.88, lat=19.07, popup="Mumbai, Maharashtra")
Urlaub <- addMarkers(Urlaub, lng=73.17, lat=22.31, popup="Vadodara, Gujarat")
Urlaub <- addMarkers(Urlaub, lng=72.57, lat=23.03, popup="Ahmedabad, Gujarat")
Urlaub <- addMarkers(Urlaub, lng=78.49, lat=17.38, popup="Hyderabad, Telangana")

Urlaub
```
